New approaches for boosting to uniformity

### 2014-10-02 assets/paperdraft/paper_draft.tex
Major textual changes to the section on uniformity metrics.

\author{
Aleksandar Bukva$^e$, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~,\newline
Andrey Ustyuzhanin$^{b,f}$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
\llap{$^e$}Faculty of Physics, Belgrade, Serbia \\
\llap{$^f$}Moscow Institute of Physics and Technology, Moscow, Russia\\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

\bibitem{Sjostrand:2006za}
{"Sj\"{o}strand, Torbj\"{o}rn and Mrenna, Stephen and Skands, Peter"},
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026},
{\emph{JHEP} {\bf 05} (2006) 026}.
[\hepph{0603175}]

\bibitem{LHCb-PROC-2010-056}
{"Belyaev, I. and others"},
\emph{Handling of the generation of primary events in GAUSS, the LHCb simulation framework},
\href{http://dx.doi.org/10.1109/NSSMIC.2010.5873949},
{\emph{NSS/MIC} {\bf IEEE} (2010) 1155}.

\bibitem{Lange:2001uf}
{"Lange, D. J."},
\emph{The EvtGen particle decay simulation package},
\href{http://dx.doi.org/10.1016/S0168-9002(01)00089-4},
{\emph{NIM} {\bf A462} (2001) 152-155}.

\bibitem{Golonka:2005pn}
{"Golonka, Piotr and Was, Zbigniew"},
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4},
{\emph{EPJ} {\bf C45} (2006) 97-107}.
[\hepph{0506026}]

\bibitem{Allison:2006ve}
{"Allison, John and Amako, K. and Apostolakis, J. and Araujo, H. and Dubois, P.A. and others"},
\emph{Geant4 developments and applications},
\href{http://dx.doi.org/10.1109/TNS.2006.869826},
{\emph{IEEE TNS} {\bf 53} (2006) 270}.

\bibitem{Agostinelli:2002hh}
{"Agostinelli, S. and others"},
\emph{Geant4: a simulation toolkit},
\href{http://dx.doi.org/10.1016/S0168-9002(03)01368-8},
{\emph{NIM} {\bf A506} (2003) 250}.

\bibitem{LHCb-PROC-2011-006}
{"Clemencic, M and others"},
\emph{The LHCb simulation application, GAUSS : design, evolution and experience},
\href{http://dx.doi.org/10.1088/1742-6596/331/3/032023},
{\emph{J. Phys. Conf. Ser.} {\bf 331} (2011) 032023}.

@@

\appendix
\section{Other Flatness Loss Criteria}

Clean all this up...

%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
\input{parts/approaches}

>>>>

\author{
Aleksandar Bukva$^e$, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~,\newline
Andrey Ustyuzhanin$^{b,f,g}$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
\llap{$^e$}Faculty of Physics, Belgrade, Serbia \\
\llap{$^f$}Moscow Institute of Physics and Technology, Moscow, Russia\\
\llap{$^g$}Imperial College, London, UK\\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

\bibitem{Sjostrand:2006za}
{"Sj\"{o}strand, Torbj\"{o}rn and Mrenna, Stephen and Skands, Peter"},
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026}
{\emph{JHEP} {\bf 05} (2006) 026}.
[\hepph{0603175}]

\bibitem{LHCb-PROC-2010-056}
{"Belyaev, I. and others"},
\emph{Handling of the generation of primary events in GAUSS, the LHCb simulation framework},
\href{http://dx.doi.org/10.1109/NSSMIC.2010.5873949}
{\emph{NSS/MIC} {\bf IEEE} (2010) 1155}.

\bibitem{Lange:2001uf}
{"Lange, D. J."},
\emph{The EvtGen particle decay simulation package},
\href{http://dx.doi.org/10.1016/S0168-9002(01)00089-4}
{\emph{NIM} {\bf A462} (2001) 152-155}.

\bibitem{Golonka:2005pn}
{"Golonka, Piotr and Was, Zbigniew"},
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4}
{\emph{EPJ} {\bf C45} (2006) 97-107}.
[\hepph{0506026}]

\bibitem{Allison:2006ve}
{"Allison, John and Amako, K. and Apostolakis, J. and Araujo, H. and Dubois, P.A. and others"},
\emph{Geant4 developments and applications},
\href{http://dx.doi.org/10.1109/TNS.2006.869826}
{\emph{IEEE TNS} {\bf 53} (2006) 270}.

\bibitem{Agostinelli:2002hh}
{"Agostinelli, S. and others"},
\emph{Geant4: a simulation toolkit},
\href{http://dx.doi.org/10.1016/S0168-9002(03)01368-8}
{\emph{NIM} {\bf A506} (2003) 250}.

\bibitem{LHCb-PROC-2011-006}
{"Clemencic, M and others"},
\emph{The LHCb simulation application, GAUSS : design, evolution and experience},
\href{http://dx.doi.org/10.1088/1742-6596/331/3/032023}
{\emph{J. Phys. Conf. Ser.} {\bf 331} (2011) 032023}.

\bibitem{ref:FS1997}
{Y. Freund, and R. Schapire},
\emph{A Decision-Theoretic Generalization of On-Line Learning and an Application to Boosting}, 
{\emph{Journal of Computer and System Sciences} {\bf 55(1)} (August 1997) 119-139}.

\bibitem{ref:F1999}
{Jerome H. Friedman},
\emph{Greedy Function Approximation: A Gradient Boosting Machine},
\href{http://statweb.stanford.edu/~jhf/ftp/trebst.pdf}
{\emph{Annals of Statistics} {\bf 29} (2000) 1189-1232}.

@@

\appendix
%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
\input{parts/approaches}

### 2014-10-02 assets/paperdraft/parts/introduction.tex
bibliography update
minor fixes in text

The one approach that was already proposed is uBoost (uniform BOOSTing) --- a modification of AdaBoost algorithm [link]

@@

The features, along which we want the prediction to be flat, will be referred to as 
``uniform variables''. In high energy physics these are usually masses.

>>>>

The one approach that was already proposed is uBoost (uniform BOOSTing) --- a modification of AdaBoost algorithm~\cite{ref:FS1997}

@@

The features, along which we want the prediction to be flat, will be referred to as 
\textit{uniform variables}. In high energy physics these are usually masses.
